---
title: "Untitled"
author: "a"
date: "April 23, 2019"
output:
  html_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library("plotly")
library("tidyverse")
library("data.table")
library("gridExtra")
library("knitr")
library(readr)
library(randomForest)
library(MASS)
library(corrplot)
library(dplyr)
```


```{r}

olympics<-read_csv("C:/Users/A/Desktop/632Regression/Project/DatasetPractice/olympics_1980_subset.csv",
                 col_types = cols(
                   Sex = col_factor(levels = c("M","F")),
                   Age =  col_integer(),
                   Height = col_double(),
                   Weight = col_double(),
                   NOC = col_character(),
                   Year = col_integer(),
                   Season = col_factor(levels = c("Summer","Winter")),
                   City = col_character(),
                   Sport = col_character()
                 )
)

```

```{r}
olympics2 <- na.omit(olympics)
olympics3 <- olympics2[which(olympics2$Year >= 1980), ]
```


```{r}
# make a dummy variable for Swimming
n = nrow(olympics3)
swim <- rep(0, n)
ind <- which(olympics3$Sport == "Swimming")
swim[ind] <- 1
olympics3$swim01 = swim
```

```{r}
n = nrow(olympics3)
equestrianism <- rep(0, n)
ind <- which(olympics3$Sport == "Equestrianism")
equestrianism[ind] <- 1
olympics3$equestrianism01 = equestrianism
```


```{r}
n = nrow(olympics3)
archery <- rep(0, n)
ind <- which(olympics3$Sport == "Archery")
archery [ind] <- 1
olympics3$archery01 = archery
```


```{r}
n = nrow(olympics3)
athletics <- rep(0, n)
ind <- which(olympics3$Sport == "Athletics")
athletics [ind] <- 1
olympics3$athletics01 = athletics
```


```{r}
n = nrow(olympics3)
badminton <- rep(0, n)
ind <- which(olympics3$Sport == "Badminton")
badminton [ind] <- 1
olympics3$badminton01 = badminton
```


```{r}
n = nrow(olympics3)
basketball <- rep(0, n)
ind <- which(olympics3$Sport == "Basketball")
basketball  [ind] <- 1
olympics3$basketball01 = basketball 
```


```{r}
n = nrow(olympics3)
beachvolleyball <- rep(0, n)
ind <- which(olympics3$Sport == "Beach Volleyball")
beachvolleyball[ind] <- 1
olympics3$beachvolleyball01 = beachvolleyball
```

```{r}
n = nrow(olympics3)
boxing <- rep(0, n)
ind <- which(olympics3$Sport == "Boxing")
boxing [ind] <- 1
olympics3$boxing01 = boxing
```

```{r}
n = nrow(olympics3)
canoeing <- rep(0, n)
ind <- which(olympics3$Sport == "Canoeing")
canoeing [ind] <- 1
olympics3$canoeing01 = canoeing
```

```{r}
n = nrow(olympics3)
cycling <- rep(0, n)
ind <- which(olympics3$Sport == "Cycling")
cycling [ind] <- 1
olympics3$cycling01 = cycling
```

```{r}
n = nrow(olympics3)
diving <- rep(0, n)
ind <- which(olympics3$Sport == "Diving")
diving [ind] <- 1
olympics3$diving01 = diving
```

```{r}
n = nrow(olympics3)
fencing <- rep(0, n)
ind <- which(olympics3$Sport == "Fencing")
fencing [ind] <- 1
olympics3$fencing01 = fencing
```


```{r}
n = nrow(olympics3)
football <- rep(0, n)
ind <- which(olympics3$Sport == "Football")
football [ind] <- 1
olympics3$football01 = football
```

```{r}
n = nrow(olympics3)
golf <- rep(0, n)
ind <- which(olympics3$Sport == "Golf")
golf [ind] <- 1
olympics3$golf01 = golf
```

```{r}
n = nrow(olympics3)
gymnastics <- rep(0, n)
ind <- which(olympics3$Sport == "Gymnastics")
gymnastics [ind] <- 1
olympics3$gymnastics01 = gymnastics
```

```{r}
n = nrow(olympics3)
handball <- rep(0, n)
ind <- which(olympics3$Sport == "Handball")
handball [ind] <- 1
olympics3$handball01 = handball
```

```{r}
n = nrow(olympics3)
hockey <- rep(0, n)
ind <- which(olympics3$Sport == "Hockey")
hockey [ind] <- 1
olympics3$hockey01 = hockey
```

```{r}
n = nrow(olympics3)
judo <- rep(0, n)
ind <- which(olympics3$Sport == "Judo")
judo [ind] <- 1
olympics3$judo01 = judo
```

```{r}
n = nrow(olympics3)
modernpentathlon <- rep(0, n)
ind <- which(olympics3$Sport == "Modern Pentathlon")
modernpentathlon [ind] <- 1
olympics3$modernpentathlon01 = modernpentathlon
```

```{r}
n = nrow(olympics3)
rhythmicgymnastics <- rep(0, n)
ind <- which(olympics3$Sport == "Rhythmic Gymnastics")
rhythmicgymnastics [ind] <- 1
olympics3$rhythmicgymnastics01 = rhythmicgymnastics
```


```{r}
n = nrow(olympics3)
rowing <- rep(0,n)
ind <- which(olympics3$Sport == "Rowing")
rowing [ind] <- 1
olympics3$rowing01 = rowing
```

```{r}
n = nrow(olympics3)
rugbysevens <- rep(0, n)
ind <- which(olympics3$Sport == "Rugby Sevens")
rugbysevens [ind] <- 1
olympics3$rugbysevens01 = rugbysevens
```

```{r}
n = nrow(olympics3)
sailing <- rep(0, n)
ind <- which(olympics3$Sport == "Sailing")
sailing [ind] <- 1
olympics3$sailing01 = sailing
```

```{r}
n = nrow(olympics3)
shooting <- rep(0, n)
ind <- which(olympics3$Sport == "Shooting")
shooting [ind] <- 1
olympics3$shooting01 = shooting
```

```{r}
n = nrow(olympics3)
softball <- rep(0, n)
ind <- which(olympics3$Sport == "Softball")
softball [ind] <- 1
olympics3$softball01 = softball
```

```{r}
n = nrow(olympics3)
synchronizedswimming <- rep(0, n)
ind <- which(olympics3$Sport == "Synchronized Swimming")
synchronizedswimming [ind] <- 1
olympics3$synchronizedswimming01 = synchronizedswimming
```

```{r}
n = nrow(olympics3)
tabletennis <- rep(0, n)
ind <- which(olympics3$Sport == "Table Tennis")
tabletennis [ind] <- 1
olympics3$tabletennis01 = tabletennis
```


```{r}
n = nrow(olympics3)
taekwondo <- rep(0, n)
ind <- which(olympics3$Sport == "Taekwondo")
taekwondo [ind] <- 1
olympics3$taekwondo01 = taekwondo
```

```{r}
n = nrow(olympics3)
tennis <- rep(0, n)
ind <- which(olympics3$Sport == "Tennis")
tennis [ind] <- 1
olympics3$tennis01 = tennis
```

```{r}
n = nrow(olympics3)
triathlon <- rep(0, n)
ind <- which(olympics3$Sport == "Triathlon")
triathlon [ind] <- 1
olympics3$triathlon01 = triathlon
```

```{r}
n = nrow(olympics3)
volleyball <- rep(0, n)
ind <- which(olympics3$Sport == "Volleyball")
volleyball [ind] <- 1
olympics3$volleyball01 = volleyball
```

```{r}
n = nrow(olympics3)
waterpolo <- rep(0, n)
ind <- which(olympics3$Sport == "Water Polo")
waterpolo [ind] <- 1
olympics3$waterpolo01 = waterpolo
```

```{r}
n = nrow(olympics3)
weightlifting <- rep(0, n)
ind <- which(olympics3$Sport == "Weightlifting")
weightlifting [ind] <- 1
olympics3$weightlifting01 = weightlifting
```

```{r}
n = nrow(olympics3)
wrestling <- rep(0, n)
ind <- which(olympics3$Sport == "Wrestling")
wrestling [ind] <- 1
olympics3$wrestling01 = wrestling
```

```{r}
n = nrow(olympics3)
male <- rep(0, n)
ind <- which(olympics3$Sex == "M")
male [ind] <- 1
olympics3$male01 = male
```

```{r}
n = nrow(olympics3)
female <- rep(0, n)
ind <- which(olympics3$Sex == "F")
female [ind] <- 1
olympics3$female01 = female
```



```{r}
# eval = F (don't evaluate the code in this chunk again because the individual previous code chunks have been executed) and echo = T (display code of this chunk in the output document)
dim(olympics3)
set.seed(10)
rf1 <- randomForest(Age ~ male01 + female01 +Height + Weight + Year  +archery01+athletics01+badminton01+basketball01+beachvolleyball01+boxing01+canoeing01+cycling01+diving01+equestrianism01+fencing01+football01+golf01+ gymnastics01+ handball01+hockey01+judo01+modernpentathlon01+rowing01+rhythmicgymnastics01+rugbysevens01+sailing01+shooting01+softball01+swim01+synchronizedswimming01+tabletennis01+taekwondo01+tennis01+triathlon01+volleyball01+waterpolo01+weightlifting01+wrestling01,data = olympics3, ntree=500, importance=TRUE)
rf1
#saveRDS(rf1, file="C:/Users/A/Desktop/632Regression/Project/Code/rf1.rds")
```


```{r}
plot(predict(rf1), olympics3$Age, xlab="OOB Predictions (Age)", ylab="Observed Values (Age)",xlim=c(5,50),ylim=c(5,50))
abline(0,1, col="red", lwd=2)
```

```{r}
plot(rf1)
```


```{r}
importance(rf1)
```

```{r}
varImpPlot(rf1, type=1)
```

Top 10 Most Predictive Features for Age: Year, Equestrianism, Shooting, Swim, Sailing, Football, Weight, Cycling, athletics, and Height, respectively.  


```{r}
# Determine Positive and Negative Correlations with Age
lm1<-lm(Age~ Height + Weight + Year  + archery01 + athletics01 +boxing01 +cycling01 +diving01 +equestrianism01 +fencing01 +football01 + gymnastics01 +rowing01 +sailing01 +shooting01 +swim01 +synchronizedswimming01 +tabletennis01 +tennis01+ canoeing01, data = olympics3)
summary(lm1)
```


# The Strongest Positive correlations with Age listed as: Year, Equestrianism, Shooting, Sailing, Weight, Cycling, Athletics, Fencing, Rowing, Table Tennis, and Archery, respectively.  

# The Strongest Negative Correlations with Age listed as: Swim, Football, Height, Diving, Gymnastics, Tennis, Boxing, Synchronized Swim and Canoeing, respectively.
